---
title: "MSDS 6306: Case 1 "
author:
  - "Blake Holmes and Mel Schwan"
date: "June 27, 2019"
output: 
  html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(officer)
library(magrittr)

#maps
library(spData)
library(mapdata)
library(maps)
library(stringr)
library(viridis)

```

```{r injest data, echo=TRUE}
beerData<-read_csv("./Data/Beers.csv")
breweryData<-read_csv("./Data/Breweries.csv")

```

```{r exploratory beerData analysis, echo=TRUE}
###b. What are the dimensions of the data?

glimpse(beerData)
summary(beerData)
#Name              Beer_ID            ABV               IBU           Brewery_id       Style               Ounces 

#beer summarized by style 
beerData %>%
  group_by(Style) %>%
  summarise(
    count= n(),
    IBU_count = sum(!is.na(IBU)),
    IBU_average = mean(IBU, na.rm = TRUE),
    IBU_sd = sd(IBU, na.rm = TRUE),
    ABV_count = sum(!is.na(ABV)),
    ABV_average = mean(ABV, na.rm = TRUE),
    ABV_sd = sd(ABV, na.rm = TRUE), 
    Ounces_count = sum(!is.na(Ounces)),
    Ounces_average = mean(Ounces, na.rm = TRUE),
    Ounces_sd = sd(Ounces, na.rm = TRUE)
  ) 

#Percentage of missing values in dataset
paste0("The total number of beers is: ", nrow(beerData))

percent_missing<-beerData %>% 
  summarise_all(funs(100*sum(is.na(.))/nrow(beerData))) %>% #count the number of NAs or blanks divided by total rows
  round(2) %>% 
  lapply(function(x){paste0(x,"%")}) %>%
  as_tibble()
missing_info <- paste('  ABV >', percent_missing$ABV, '  IBU >', percent_missing$IBU, '  Style >', percent_missing$Style)
# ABV, IBU, Style have missing values 

#hmm what should be done about the missing values...
```

```{r exploratory brewery data aggregation by state, echo=TRUE}

glimpse(breweryData)
summary(breweryData)
#    Brew_ID          Name               City              State          

#Report the number of NA's in each column.
breweryData %>% 
  summarise_all(funs(sum(is.na(.))))#count the number of NAs or blanks
#no missing values 
```

```{r get population data, echo=TRUE}

library("httr")
library("jsonlite")


#2018 projected population data
pop_url <- "https://api.census.gov/data/2018/pep/population?get=POP,GEONAME&for=state"

statepop_raw<- pop_url %>% 
  GET() %>% 
  content("text") %>%
  fromJSON(flatten=TRUE) %>% 
  as_tibble() %>% 
  slice(2:n())#remove the first row which is the labels 

names(statepop_raw)<-c("Population","State","State_ID")

statepop_raw$Population<- as.integer(statepop_raw$Population)

#add state abbreviations and DC/puerto rico
statepop_raw$State_Abb <- c(sort(c("DC",state.abb)),"PR")

```

```{r get state area data, echo=TRUE}
library(rvest)

area_url <-"https://en.wikipedia.org/wiki/List_of_U.S._states_and_territories_by_area"

statearea<- area_url %>% 
  read_html() %>% 
  html_node('#mw-content-text > div > table:nth-child(6)') %>% 
  html_table(header = F) %>% 
  slice(3:n()) %>% #remove the two rows which are labels
  select(X1,X6) %>% #keep the state area excluding water
  rename("State_name"="X1","Square_miles"="X6") %>% 
  mutate(Square_miles=as.numeric(gsub(",", "", Square_miles))) #remove thousands separator ","
  
```

#How many breweries in each state

```{r how many breweries in each state, echo=TRUE}
brewstate<-breweryData %>% 
  group_by(State) %>% 
  summarise(Number_of_breweries=n()) %>% 
  arrange(desc(Number_of_breweries))

top_brewstate <- head(brewstate,5) 
bottom_brewstate <- tail(brewstate,5)

top_brewstate
bottom_brewstate
```
# Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.

```{r merge data, echo=TRUE}

beer_brewery<-beerData %>%
  left_join(breweryData, by=c("Brewery_id"="Brew_ID"), suffix = c(".beer", ".brewery")) %>% 
  rename(Beer_name=Name.beer, Brewery_name=Name.brewery) %>% 
  #separate continuous variables into 3 groups, low/medium/high
  mutate(ABV_rating= cut_number(ABV, n = 3,labels=c("low","medium","high"))) %>% 
  mutate(IBU_rating= cut_number(IBU, n = 3,labels=c("low","medium","high"))) 
  
beer_brewery %>% 
  filter(is.na(Brewery_name)) 
#returns no results so all beers have a brewery

#Post merge data peak 
first_combo_brewery<-head(beer_brewery,6)
last_combo_brewery<-tail(beer_brewery,6)


```



```{r looking for bad data, echo=FALSE}
#looking for duplicated data in character vectors
lookForDupStrings <- function(string_arr){
  library(tidystringdist)
  string_arr %>%
    unique() %>% 
    tidy_comb_all() %>% 
    tidy_stringdist() %>% 
    arrange(osa)
}

lookForDupStrings(beer_brewery$Beer_name)
#there are a lot of simliar beer names, including those just differing by year.
#however it looks like good data
lookForDupStrings(beer_brewery$Style)
#these look pretty good

lookForDupStrings(beer_brewery$Brewery_name)
#TODO(bjh) there are duplicated breweries for cleanup, for example
#breweryData %>% filter(str_detect(Name,"Grain"))
#  Brew_ID Name                          City       State
#     <int> <chr>                         <chr>      <chr>
# 1       2 Against the Grain Brewery     Louisville KY   
# 2      63 Against The Grain Brewery     Louisville KY   
```

# Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.
```{r Aggregations by State, echo=TRUE}

#Summary data by State 
beer_brewery_byState<-beer_brewery %>%
  group_by(State) %>%
  summarise(
    Number_of_beers= n(),
    Number_of_breweries=length(unique(Brewery_name)),
    Number_of_styles=length(unique(Style)),
    IBU_count = sum(!is.na(IBU)),
    IBU_average = mean(IBU, na.rm = TRUE),
    IBU_median = median(IBU, na.rm = TRUE),
    IBU_sd = sd(IBU, na.rm = TRUE),
    ABV_count = sum(!is.na(ABV)),
    ABV_average = mean(ABV, na.rm = TRUE),
    ABV_median = median(ABV, na.rm = TRUE),
    ABV_sd = sd(ABV, na.rm = TRUE),
    Ounces_count = sum(!is.na(Ounces)),
    Ounces_average = mean(Ounces, na.rm = TRUE),
    Ounces_median = median(Ounces, na.rm = TRUE),
    Ounces_sd = sd(Ounces, na.rm = TRUE),
  )

#add counts for Ounces
beer_brewery_byState<-beer_brewery %>%
  filter(!is.na(Ounces)) %>% 
  count(State,Ounces) %>% 
  spread(Ounces,n, fill=0,sep = "_") %>% 
  right_join(beer_brewery_byState, by="State")

#add category counts for ABV_rating
beer_brewery_byState<-beer_brewery %>%
  filter(!is.na(ABV_rating)) %>% 
  count(State,ABV_rating) %>% 
  spread(ABV_rating,n, fill=0,sep = "_") %>%
  right_join(beer_brewery_byState, by="State")

#add category counts for IBU_rating
beer_brewery_byState<-beer_brewery %>%
  filter(!is.na(IBU_rating)) %>% 
  count(State,IBU_rating) %>% 
  spread(IBU_rating,n, fill=0,sep = "_") %>% 
  right_join(beer_brewery_byState, by="State") 

#add in population values
beer_brewery_byState<-beer_brewery_byState %>% 
  left_join(y=statepop_raw, by=c("State"="State_Abb")) %>% 
  select(c(-State_ID)) %>% 
  rename(State_name=State.y) %>% 
  mutate(breweries_per_million_person=(1000000*Number_of_breweries/Population))

#add in state area in Square_miles
beer_brewery_byState<-beer_brewery_byState %>% 
  left_join(y=statearea, by="State_name") %>% 
  mutate(breweries_per_thousand_sqmiles=(1000*Number_of_breweries/Square_miles))

```

```{r prepare data for mapping, echo=TRUE}

states <- map_data("state")

map_data<-beer_brewery_byState %>% 
  mutate(State_name=tolower(State_name)) %>%  #to match the state mapping data
  right_join(states, by=c("State_name"="region"))

state_base <- ggplot(data = map_data, mapping = aes(x = long, y = lat, group = group)) +
      geom_polygon(color = "black", fill = "gray") + 
      theme_void()

```

```{r state maps, echo=TRUE}

state_base +
      geom_polygon(data = map_data, aes(fill = Population)) #TODO(BJH) think about breaking into subregions 

library(grid)
library(gridExtra)

#Example on how to arrange multiple plots 

#General Statistics
general_statistics<-grid.arrange(
    state_base + geom_polygon(data = map_data, aes(fill = Number_of_breweries)) +
      scale_fill_viridis(option="D"),
    state_base + geom_polygon(data = map_data, aes(fill = Number_of_beers)) +
      scale_fill_viridis(option="D"),
    state_base + geom_polygon(data = map_data, aes(fill = Number_of_styles)) +
      scale_fill_viridis(option="D"),
    state_base + geom_polygon(data = map_data, aes(fill = Ounces_median)) +
      scale_fill_viridis(option="D"),
    state_base + geom_polygon(data = map_data, aes(fill = breweries_per_million_person)) +
      scale_fill_viridis(option="D"),
    state_base + geom_polygon(data = map_data, aes(fill = Population/1000000))  + labs(fill = "Population (millions)") + scale_fill_viridis(option="D"),
    ncol=3, nrow=2
)
ggsave('Export/brewers_ratings.jpg')
#ABV data mapped 
grid.arrange(
  state_base + geom_polygon(data = map_data, aes(fill = ABV_rating_high)) + scale_fill_viridis(option="D"), 
  state_base + geom_polygon(data = map_data, aes(fill = ABV_rating_medium)) + scale_fill_viridis(option="D"), 
  state_base + geom_polygon(data = map_data, aes(fill = ABV_rating_low))+ scale_fill_viridis(option="D"),  
  state_base + geom_polygon(data = map_data, aes(fill = ABV_sd)) + scale_fill_viridis(option="D"),
  state_base + geom_polygon(data = map_data, aes(fill = ABV_median)) + scale_fill_viridis(option="D"),
    ncol=3, nrow=2
)

ggsave('Export/abv_ratings.jpg')
#IBU data mapped 
grid.arrange(
  state_base + geom_polygon(data = map_data, aes(fill = IBU_rating_high)) + scale_fill_viridis(option="D"), 
  state_base + geom_polygon(data = map_data, aes(fill = IBU_rating_medium)) + scale_fill_viridis(option="D"), 
  state_base + geom_polygon(data = map_data, aes(fill = IBU_rating_low))+ scale_fill_viridis(option="D"),  
  state_base + geom_polygon(data = map_data, aes(fill = IBU_sd)) + scale_fill_viridis(option="D"),
  state_base + geom_polygon(data = map_data, aes(fill = IBU_median)) + scale_fill_viridis(option="D"),
    ncol=3, nrow=2
)
ggsave('Export/ibu_ratings.jpg')

state_base +
      geom_polygon(data = map_data, aes(fill = Ounces_median))
ggsave('Export/Ounces_data.jpg')


#MAPPING ABV BY STATE
grid.arrange(
  #HIGH ABV Beers per million people
  state_base +
      geom_polygon(data = map_data, aes(fill = ABV_rating_high), show.legend = FALSE) + 
      scale_fill_continuous(name = "High ABV Beers"), 
  #MEDIUM ABV Beers per million people
  state_base +
      geom_polygon(data = map_data, aes(fill = ABV_rating_medium), show.legend = FALSE) + 
      scale_fill_continuous(name = "Medium ABV Beers"),  
  #LOW ABV Beers per million people
  state_base +
      geom_polygon(data = map_data, aes(fill = ABV_rating_low),show.legend = FALSE) + 
    scale_fill_continuous(name = "Low ABV Beers"),
  #HIGH ABV Beers per million people
  state_base +
      geom_polygon(data = map_data, aes(fill = (1000000*ABV_rating_high)/Population),show.legend = FALSE)+
      scale_fill_continuous(name = "High ABV beers per million people"),
  #MEDIUM ABV Beers per million people
  state_base +
      geom_polygon(data = map_data, aes(fill = (1000000*ABV_rating_medium)/Population),show.legend = FALSE)+
      scale_fill_continuous(name = "Medium ABV beers per million people"),
  #LOW ABV Beers per million people
  state_base +
      geom_polygon(data = map_data, aes(fill = (1000000*ABV_rating_low)/Population),show.legend = FALSE)+
      scale_fill_continuous(name = "Low ABV beers per million people")  
  ,ncol=3, nrow=2
) %>% 
  ggsave(filename = "Export/ABV_by_state.jpg")



ggsave('Export/ABV_high_data.jpg')



ggsave('Export/ABV_medium_data.jpg')


ggsave('Export/ABV_low_data.jpg')

 
      scale_fill_continuous(name = "Number of Low ABV Beers")  

ggsave('Export/ABV_low_data.jpg')

state_base +
      geom_polygon(data = map_data, aes(fill = ABV_sd))
ggsave('Export/ABV_SD_data.jpg')

state_base +
      geom_polygon(data = map_data, aes(fill = IBU_rating_high))
ggsave('Export/ibu_high_data.jpg')

state_base +
      geom_polygon(data = map_data, aes(fill = IBU_rating_medium))
ggsave('Export/ibu_med_data.jpg')

state_base +
      geom_polygon(data = map_data, aes(fill = IBU_rating_low))
ggsave('Export/ibu_low_data.jpg')

state_base +
      geom_polygon(data = map_data, aes(fill = IBU_sd))
ggsave('Export/ibu_SD_data.jpg')
```


```{r IBU Plots, echo=TRUE}
#top 10 states for having high IBU beers
top_ibu<-beer_brewery_byState %>% 
  arrange(desc(IBU_rating_high)) %>% 
  head(10)

#bottom 10 states for having high IBU beers
bottom_ibu<-beer_brewery_byState %>% 
  arrange(desc(IBU_rating_high)) %>% 
  tail(10)

#barplot of median IBU by state, maybe do the top 10 and bottom 10 becuase it's crowded
top_ibu<-beer_brewery_byState %>%
  arrange(IBU_median) %>% 
  mutate(State=factor(State, levels=State)) %>%
  head(10) %>% 
  ggplot(aes(x=State, y=IBU_median)) + geom_col()+ 
  labs(title="States with Highest IBU", 
       subtitle="", y="Median IBU")

ggsave('Export/Hi_median_alch.jpg')
  
beer_brewery_byState %>%
  arrange(desc(IBU_median)) %>% 
  mutate(State=factor(State, levels=State)) %>%
  head(10) %>% 
  ggplot(aes(x=State, y=IBU_median)) + geom_col() + 
  labs(title="States with Lowest IBU", 
       y="IBU")

ggsave('Export/Low_median_alch.jpg')
```

```{r ABV Plots, echo=TRUE}
#barplot of median ABV by state, maybe do the top 10 and bottom 10 because it's crowded
beer_brewery_byState %>%
  arrange(ABV_median) %>% #lowest to highest
  mutate(State=factor(State, levels=State)) %>%# To set the order appropriately for the plot
  head(10) %>% 
  ggplot(aes(x=State, y=ABV_median)) + geom_col() + 
  coord_flip()+ 
  labs(title="States with Lowest ABV", 
       y="ABV")
ggsave('Export/bottom_abv_summary.jpg')

beer_brewery_byState %>%
  arrange(desc(ABV_median)) %>% #highest to lowers 
  mutate(State=factor(State, levels=State)) %>% # To set the order appropriately for the plot
  head(10) %>% 
  ggplot(aes(x=State, y=ABV_median)) + geom_col() + 
  coord_flip() + 
  labs(title="States with Highest ABV", 
       y="ABV")
ggsave('Export/top_abv_summary.jpg')
```

```{r relationship between IBU and ABV, echo=TRUE}
#BASIC POSITIVE CORRELATION 

beer_brewery %>% 
  ggplot(aes(x=IBU, y=ABV)) + geom_point()+ 
    labs(title="ABV and IBU Scatterplot")


#WITH MARKER INDICATING MARKET OPPORTUNITY
beer_brewery %>% 
  ggplot(aes(x=IBU, y=ABV)) + 
  geom_point() + 
  annotate("rect", xmin=c(50), xmax=c(120), ymin=c(.035) , ymax=c(.06), alpha=0.2, color="blue", fill="blue") + 
  annotate("text", label="Opportunity", x=c(70), y=c(.04), color="Blue")+ 
    labs(title="ABV and IBU Scatterplot", 
       subtitle="Market Opportunity")

ggsave('Export/ibu_abv_scat.jpg')
```

```{r OUNCES relationships, echo=TRUE}
  beer_brewery %>% 
    ggplot(aes(x=Ounces, y=IBU)) + geom_point(position = "jitter")+ 
      labs(title="IBU and OUNCES Scatterplot")

 beer_brewery %>% 
  ggplot(aes(x=Ounces, y=IBU)) + geom_point(position = "jitter")+ 
    labs(title="IBU and OUNCES Scatterplot")

```

```{r relationship between Ounces and ABV, echo=TRUE}
beer_brewery %>% 
  ggplot(aes(x=Ounces, y=ABV)) + geom_point(position = "jitter") + 
   labs(title="ABV and OUNCES Scatterplot")
```

# Which state has the maximum alcoholic (ABV) beer? 

```{r maximum alcoholic (ABV) beer, echo=TRUE}

#top 10 states for having high ABV beers
top_abv<-beer_brewery_byState %>% 
  arrange(desc(ABV_rating_high)) %>% 
  rename_all(funs(str_replace_all(., "_", " "))) %>% 
  head(10)
```

# Which state has highest variance in ABV?

```{r most bitter(IBU) beer, echo=TRUE}

#top 10 states with the most variance in ABV
top_abv_sd<-beer_brewery_byState %>% 
  arrange(desc(ABV_sd)) %>% 
  rename_all(funs(str_replace_all(., "_", " "))) %>% 
  head(10)

#top 10 states with the least variance in ABV
bottom_abv_sd<-beer_brewery_byState %>% 
  arrange(ABV_sd) %>% 
  rename_all(funs(str_replace_all(., "_", " "))) %>% 
  head(10)
```


# Which states have the most and least variance in beers?
```{r most and least variance in ABV, echo=TRUE}

#top 10 states with the most variance in ABV
top_abv_sd<-beer_brewery_byState %>% 
  arrange(desc(ABV_sd)) %>% 
  rename_all(funs(str_replace_all(., "_", " "))) %>% 
  head(10)

#top 10 states with the least variance in ABV
bottom_abv_sd<-beer_brewery_byState %>% 
  arrange(ABV_sd) %>% 
  rename_all(funs(str_replace_all(., "_", " "))) %>% 
  head(10)
```

```{r most and least variance in IBU, echo=TRUE}
#top 10 states for having high IBU beers
top_ibu<-beer_brewery_byState %>% 
  arrange(desc(IBU_rating_high)) %>% 
  rename_all(funs(str_replace_all(., "_", " "))) %>% 
  head(10)

#top 10 states with the most variance in IBU
top_ibu_sd<-beer_brewery_byState %>% 
  arrange(desc(IBU_sd)) %>% 
  rename_all(funs(str_replace_all(., "_", " "))) %>% 
  head(10)

#top 10 states with the least variance in IBU
bottom_ibu_sd<-beer_brewery_byState %>% 
  arrange(IBU_sd) %>% 
  rename_all(funs(str_replace_all(., "_", " "))) %>% 
  head(10)
```

#Summary statistics for the IBU variable.

```{r summary statistics for the IBU variable, echo=TRUE}

summary(beerData$IBU)

ggplot(beerData, aes(x=IBU)) +
     geom_histogram(position="identity", alpha=0.5)+
     geom_vline(data=beerData,aes(xintercept=median(beerData$IBU)),linetype="dashed")+
     labs(title="International Bitterness Unit(IBU) Histogram",x="IBU", y = "Count") + 
     geom_vline(aes(xintercept = median(IBU, na.rm=T)),linetype="dotted", color="black") + annotate("text", x = c(33), y = c(120), label = c(paste("Median", median(beerData$IBU, na.rm=T))) , color="black", size=5 , angle=90, fontface="bold")
ggsave('Export/IBU_by_volume.jpg')

```

#Summary statistics for the ABV variable.

```{r summary statistics for the ABV variable, echo=TRUE}

summary(beerData$ABV)

ggplot(beerData, aes(x=ABV)) +
     geom_histogram(position="identity", alpha=0.5)+
     geom_vline(data=beerData,aes(xintercept=median(beerData$ABV)),linetype="dashed")+
     labs(title="Alcohol By Volume(ABV) Histogram",x="ABV", y = "Count") + 
     geom_vline(aes(xintercept = median(ABV, na.rm=T)),linetype="dotted", color="black") + annotate("text", x = c(.053), y = c(150), label = c(paste("Median", median(beerData$ABV, na.rm=T))) , color="black", size=5 , angle=90, fontface="bold")
ggsave('Export/abv_by_volume.jpg')
```
 
  
# This code produces a custom Powerpoint generating slides with data calculated and plotted above
  
```{r generation of PowerPoint slides, echo=TRUE}

#Read baseline PowerPoint file
my_pres <- read_pptx('Visuals/presentation.pptx') 
#view(layout_summary(my_pres))
#view(layout_properties(my_pres))

# States with the most brewries
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>%
  ph_with(value = "States With the Most Breweries", location = ph_location(left = 3, top = .5, width = 8, height = 1)) %>%
  ph_with_table_at(value = top_brewstate,
                   height = 5, width = 8, left = 3, top = 2,
                   last_row = FALSE, last_column = FALSE, first_row = TRUE)

# States with the least breweries
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>%
  ph_with(value = "States With the Least Breweries", location = ph_location(left = 3, top = .5, width = 8, height = 1)) %>%
  ph_with_table_at(value = bottom_brewstate,
                   height = 5, width = 8, left = 3, top = 2,
                   last_row = FALSE, last_column = FALSE, first_row = TRUE)

# Merged breweries data first six
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>%
  ph_with(value = "First Breweries Combined Beer", location = ph_location(left = 3, top = .5, width = 8, height = 1)) %>%
  ph_with_table_at(value = first_combo_brewery,
                   height = 4.0, width = 12, left = .5, top = 1,
                   last_row = FALSE, last_column = FALSE, first_row = TRUE)

# Merged breweries data last six
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>%
  ph_with(value = "Last Breweries Combined Beer", location = ph_location(left = 3, top = .5, width = 8, height = 1)) %>%
  ph_with_table_at(value = last_combo_brewery,
                   height = 4.0, width = 12, left = .5, top = 1,
                   last_row = FALSE, last_column = FALSE, first_row = TRUE)
# How many NA's were found
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "What Data Was Missing?", location = ph_location(left = 3.5, top = .5, width = 8, height = 1)) %>%
  ph_with(value = missing_info, location = ph_location(left = 2.5, top = 3, width = 12, height = 1))

#Compute the population, breweries, and beer styles by state 
filename = "Export/ibu_SD_data.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "States IBU Standard Deviation", location = ph_location(left = 3, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename, width = 10, height = 6), 
          location = ph_location(left = 1.5, top = 1, width = 10, height = 6)) 

#Compute ibu high 
filename = "Export/ibu_high_data.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "States IBU High", location = ph_location(left = 3, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename, width = 10, height = 6), 
          location = ph_location(left = 1.5, top = 1, width = 10, height = 6)) 

#Compute ibu ratings 
filename = "Export/ibu_ratings.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "States IBU Ratings", location = ph_location(left = 3, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename, width = 10, height = 6), 
          location = ph_location(left = 1.5, top = 1, width = 10, height = 6)) 

#Compute abv sd 
filename = "Export/abv_sd_data.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "States ABV Standard Deviation", location = ph_location(left = 3, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename, width = 10, height = 6), 
          location = ph_location(left = 1.5, top = 1, width = 10, height = 6)) 

#Compute abv high 
filename = "Export/abv_high_data.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "States ABV High", location = ph_location(left = 3, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename, width = 10, height = 6), 
          location = ph_location(left = 1.5, top = 1, width = 10, height = 6)) 

#Compute abv ratings 
filename = "Export/abv_ratings.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "States ABV Ratings", location = ph_location(left = 3, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename, width = 10, height = 6), 
          location = ph_location(left = 1.5, top = 1, width = 10, height = 6)) 

#Compute brewers ratings 
filename = "Export/brewers_ratings.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "States Brewers Ratings", location = ph_location(left = 3, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename, width = 10, height = 6), 
          location = ph_location(left = 1.5, top = 1, width = 10, height = 6)) 

#Compute the median alcohol content and international bitterness unit for each state. 
filename = "Export/Hi_median_alch.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "States with High Median ABV and IBU", location = ph_location(left = 2.5, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename, width = 8, height = 4.5), 
          location = ph_location(left = 3, top = 2, width = 8, height = 4.5)) 

# States with the max bitterness and max alcohol
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "Highest ABV & IBU by State", location = ph_location(left = 2, top = .5, width = 8, height = 1)) %>%
  ph_with(value = paste("State with the most ABV beers is ",head(top_abv,1)$State),  location = ph_location(left = 1, top = 3, width = 12, height = 1)) %>%
  ph_with(value = paste("State with the most IBU beers is ",head(top_ibu,1)$State), location = ph_location(left = 1, top = 5, width = 12, height = 1)) 

#Compute the median alcohol content and international bitterness unit for each state. 
filename1 = "Export/top_abv_summary.jpg"
filename2 = "Export/bottom_abv_summary.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "Summary ABV Top and Bottom by States", location = ph_location(left = 2.5, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename1, width = 4, height = 3.5), 
          location = ph_location(left = 1, top = 2, width = 5, height = 4.5)) %>%
  ph_with(external_img(src = filename2, width = 4, height = 3.5), 
          location = ph_location(left = 8, top = 2, width = 5, height = 4.5)) 

#Compute alcohol by volume 
filename = "Export/abv_by_volume.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "Alcohol by Volume", location = ph_location(left = 3, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename, width = 10, height = 6), 
          location = ph_location(left = 1.5, top = 1, width = 10, height = 6)) 
#Compute bitterness by volume 
filename = "Export/ibu_by_volume.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "Bitterness by Volume", location = ph_location(left = 3, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename, width = 10, height = 6), 
          location = ph_location(left = 1.5, top = 1, width = 10, height = 6)) 

#Compute the relationship between IBU and ABV
filename = "Export/ibu_abv_scat.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>%
  ph_with(value = "Relationship Between ABV and IBU", location = ph_location(left = 2.5, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename, width = 8, height = 4.5),
          location = ph_location(left = 3, top = 2, width = 8, height = 4.5))

#Summary slide
filename = "Visuals/summary.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>%
  ph_with(value = "Summary and Opportunities", location = ph_location(left = 2.5, top = .5, width = 10, height = 1)) %>%
  ph_with(external_img(src = filename, width = 13, height = 7.5),
          location = ph_location(left = .15, top = .15, width = 13, height = 7.5))
#Repository slide
filename = "Visuals/repository.jpg"
my_pres <- add_slide(x=my_pres, layout = "Title and Content", master = "Office Theme") %>%
  ph_with(external_img(src = filename, width = 13, height = 7.5),
          location = ph_location(left = .15, top = .15, width = 13, height = 7.5))

# Print to save powerpoint
extension <- format(Sys.time(),'%b%d%H%M%S')
print(my_pres, target = paste("anheuser-budwieser", extension, "v1.pptx", sep='') )

```

